MS5130 A3 Clothing_Product_Analysis

### 2024-04-01 MS5130_A3_Clothing_Product_Analysis.qmd
Mermaid code
Added flowchart of analysis carried out using datasets and updated readme file with dataset links.

>>>>

## Flowchart of analysis using mermaid

```{mermaid}
flowchart TB
    subgraph csv1 ["myntra_products_catalog.csv"]
    end

    subgraph csv2 ["Product_Detailed_2.csv"]
    end

    subgraph csv3 ["Product_Reviews_3.csv"]
    end

    subgraph csv4 ["Location_of_brands.csv"]
    end

    csv1 -->|Read| preprocess1[Preprocessing]
    csv2 -->|Read| preprocess2[Preprocessing]
    csv3 -->|Read| preprocess3[Preprocessing]
    csv4 -->|Geocode| preprocess4[Preprocessing]

    preprocess1 --> analysis1.1[Expensive and Budget-Friendly Brands Analysis]
    preprocess1 --> analysis1.2[Gender wise product distribution]
    preprocess1 --> analysis1.3[Color wise product distribution]

    preprocess1 --> analysis2[Average price changes over time]
    preprocess2 --> analysis2[Average price changes over time]

    preprocess2 --> analysis3[Sentiment and Review Analysis]
    preprocess3 --> analysis3[Sentiment and Review Analysis]

    analysis2 --> analysis3.1[Wordcloud of top category]

    preprocess2 --> geo[Top 3 Brands by location on world map]
    preprocess4 --> geo[Top 3 Brands by location on world map]
```
